Citeopotamus

### 2012-12-08 paper/paper.tex
I believe this wraps up the background and scraper sections

\section{Dataset}\label{sec:dataset}
%TODO(aldrin)
%overview
The dataset for which we report results was collected from \textit{PLoS
Computational Biology}~\cite{plos}. PLoS (Public Library of Science) is a
nonprofit publisher that aims to accelerate progress in science. PLoS has
several journals--ONE, Biology, Medicine, Genetics, Computational Biology,
Pathogens, and Neglected Tropical Diseases--available to the public. For our
purposes we collected articles from PLoS Computational Biology, the
computational biology journal published by PLoS. We only collected articles
from this journal simply for the reason that as computer scientists it is the
most likely to be similar to computer science publications in style and in
content. We initially were interested in a corpus of computer science
publications, however we were unable to find a source that would allow us to
programmatically collect computer science publications and articles.

@@

\subsection{Scraper}
TODO(aldrin)

@@

All text inside top-level $p$ tags can be inferred to be an entire paragraph
and was placed on a single line.  The references section was separated from the
rest of the paper by a single line with only ``REFERENCES'' on it.

\subsection{Structured Paper Directory Format}\label{sec:dir_structure}
The output of the scraper is a directory that contains information about the
root paper and all the reference that were collected.  To make all the
information easily accessible to anyone without imposing any arbitrary
restrictions, the structure of the data is enforced by directory structure.

The root directory is named using the root paper's title. Inside the root
directory is a ``references'' directory.  Inside the ``references'' directory
are sub-directories named with the number of that citation. A missing directory
means that the scraper could not collect that reference's information.

Every directory that represents a paper will have at most four files:
\begin{description}
   \item[meta.txt\footnotemark{1}] Contains the title, authors, tags, categories, and abstract.
                   This is the only file required for every paper directory.
   \item[paper.txt\footnotemark{1}] The text version of the paper. This file is required for
                    the root paper.
   \item[refs.txt\footnotemark{1}] Only the references that appear at the bottom of the paper.
                   This information is duplicated in paper.txt, but placed here
                   for convenience.
   \item[paper.pdf] The pdf version of the paper.
   \item[paper.html] The HTML version of the paper. This is grabbed should
                     the paper need to be re-parsed.
\end{description}

\footnotetext[1]{These files are not required for our implementation to work}

>>>>

\section{Dataset}\label{sec:dataset}
%overview
The dataset for which we report results was collected from \textit{PLoS
Computational Biology}~\cite{plos}. PLoS (Public Library of Science) is a
nonprofit publisher that aims to accelerate progress in science. PLoS has
several journals--ONE, Biology, Medicine, Genetics, Computational Biology,
Pathogens, and Neglected Tropical Diseases--available to the public. For our
purposes we collected articles from PLoS Computational Biology, the
computational biology journal published by PLoS. We only collected articles
from this journal simply for the reason that as computer scientists it is the
most likely to be similar to computer science publications in style and in
content. We initially were interested in a corpus of computer science
publications, however we were unable to find a source that would allow us to
programmatically collect computer science publications and articles.

@@

\subsection{Scraper}
The scraper, written in python, extensively uses urllib2 and lxml.html. The
first task is to access a search landing page using urllib2. Each search result
page maintains 10 publications per page and links at the top
and bottom of the search page that lead to other search result pages. Each
publication located on a search result page is used as a root paper.
Each listing on the search result page contains metadata for the publication
listed such as title, author, and path to the HTML of the publication.
Since we are collecting this dataset programmatically, the HTML
version is easier to work with than a PDF version of the publication, which
would require OCR to extract text. Due to the structure of the page (which is
amazingly consistent), the HTML is parsed in the following sections:
\begin{itemize}
   \item Abstract
   \item Body sections and titles
   \item References
      \begin{itemize}
         \item Search pages for each references paper
         \item Pubmed page for each reference paper
         \item Abstract, Title, and Author for refererence paper from pubmed
      \end{itemize}
\end{itemize}

First, we extract the abstract text. This is made trivial with lxml's html
parser, specifically the cssselect and text\_content methods. Similarly, the
extraction of body section text and titles of publication is easily done.
Reference papers are more difficult to obtain due to the extra content that
must be fetched online. Each reference paper listing may or may not have a link
to a landing page listing various other sources where the publication may be
found. In cases where there is no link, then this listing is skipped and the
next one parsed. For cases where there is indeed a link, the pubmed source is
always picked and the provided pubmed URL to the publication is used to
retrieve the abstract, title, and authors for the reference paper. While pubmed
makes extraction of the abstract text somewhat difficult, it is solved through
the use of text\_content in python's lxml library, which grabs all text from
child nodes and removes HTML markup. As the necessary information for each
reference paper is retrieved, the reference paper is written out in the
appropriate directory location as mentioned below in section
\ref{sec:dir_structure}.

@@

All text inside top-level $p$ tags can be inferred to be an entire paragraph
which was placed on a single line. The references section was separated from the
rest of the paper by a single line with only ``REFERENCES'' on it.
Additionally, the top of the text file listed ``TITLE:'', ``AUTHORS:'', and
extra information if accessible (which was not the case for PLoS Computational
Biology, specifically ``TERMS:'' and ``CATEGORIES:'').

\subsection{Structured Paper Directory Format}\label{sec:dir_structure}
The output of the scraper is a directory that contains information about the
root paper and all collected reference papers. To make all the
information easily accessible to anyone without imposing any arbitrary
restrictions, the structure of the data is enforced by directory structure.

The root directory is named using the root paper's title. Inside the root
directory is a ``references'' directory and four or five files, described
below. Inside the ``references'' directory are sub-directories for each
citation number in the root paper. The information for reference papers are
maintained in the appropriately numbered directory, such that a reference paper
``foo'', is the fourth citation (i.e. appears in the root paper as ``[4]'')
then information for paper ``foo'' is maintained in the directory ``4'' in the
root paper's ``references'' directory. A missing directory
means that the scraper could not collect that reference's information.

Every directory that represents a paper will have at most four files:
\begin{itemize}
   \item \textbf{meta.txt}\footnotemark[1]{} -- Contains the title, authors,
                                                tags, categories, and abstract.
                                                This is the only file required
                                                for every paper directory.
   \item \textbf{paper.txt}\footnotemark[1]{} -- The text version of the paper.
                                                 This file is required for the
                                                 root paper.
   \item \textbf{refs.txt}\footnotemark[1]{} -- Only the references that appear
                                                at the bottom of the paper.
                                                This information is duplicated
                                                in paper.txt, but placed here
                                                for convenience.
   \item \textbf{paper.pdf} -- The pdf version of the paper.
   \item \textbf{paper.html} -- The HTML version of the publication. This is
                                grabbed should the paper need to be re-parsed.
\end{itemize}

\footnotetext[1]{These files \textbf{are required} for our implementation to work}
